Appendix

### 2021-04-17 R/README.Rmd
update R readme

---
title: "Reproducibility Instructions"
#author: "Hussein Mahfouz"
date: "18/8/2020"
output: github_document
fontsize: 10pt
---

@@

This repository contains the code used for the paper. Below is an explanation of the scripts used, and how the analysis can be reproduced.

@@

The paper can be found in the repo,[**ADD LINK TO PDF**]

@@

There is one file that cannot be synced to github due to its size. This file is neseccary for the scripts to run:

@@

@@

The scripts should be run in the order they are numbered in (and listed in here). The only exception is _x_dodgr_weighting_profiles.R.

@@

This script uses the The [dodgr](https://atfutures.github.io/dodgr/) package is used to route potential cycling demand onto the road network. This is done for the different weighting profiles used in the analysis

>>>>

---
title: "Reproducibility Instructions"
#author: "Hussein Mahfouz"
#date: "18/8/2020"
output: github_document
fontsize: 10pt
---

@@

This repository contains the code used for the paper. Below is an explanation of the scripts used, and how the analysis can be reproduced for other cities.

@@

The paper can be found in the repo, [here](https://github.com/Hussein-Mahfouz/cycle-networks/blob/main/README.pdf)

@@

There is one file that cannot be synced to github due to its size. This file is necessary for the scripts to run:

@@

## Reproducing the Results for Other Cities

To reproduce the results presented for other cities in the UK there are a few computing pre-requisites:

- A reasonably powerful computer, e.g. with 8 GB RAM
- The statistical programming language R installed (we recommend running it in the RStudio editor)

To ensure you have the necessary packages installed, open the `cycle-networks.Rproj` file in RStudio and run the following commands:

```{r, eval=FALSE}
install.packages("renv")
renv::restore()
```

The `build.R` script contains all of the necessary steps to reproduce the results for any city in the UK.
Open this file with the following command and run the code line-by-line.

```{r, eval=FALSE}
file.edit("R/build.R")
```

<!-- Todo: make the .zip download work for anyone, e.g. by uploading the data to the osf.io website alongside the preprint. -->

You can select a city to build by executing the following command:

```{r}
chosen_city <- "Leeds"
```

Replacing `Leeds` with any other city will make the script work for that city.
Note: this only works for Local Authority names in England and Wales listed below.

@@

Below is a description of all the scripts used to run the analysis. They are all sourced in the `build.R` script, but a description of all the scripts/components should allow any part of the analysis to be improved

The scripts are run in the order they are numbered in (and listed in here). The only exception is _x_dodgr_weighting_profiles.R.

@@

This script uses the [dodgr](https://atfutures.github.io/dodgr/) package to route potential cycling demand onto the road network. This is done for the different weighting profiles used in the analysis

### 2021-04-17 appendix.Rmd
update R readme

---
title: "Appendix"
author: "Hussein Mahfouz, Robin Lovelace, Elsa Arcaute"
date: "13/03/2021"
geometry: margin=1.5cm
output:
  pdf_document:
    extra_dependencies: ["subcaption", "float"]
---

>>>>

---
title: "Appendix"
#author: "Hussein Mahfouz, Robin Lovelace, Elsa Arcaute"
date: "13/03/2021"
geometry: margin=1.5cm
output:
  pdf_document:
    extra_dependencies: ["subcaption", "float"]
---
